
% Default to the notebook output style

    


% Inherit from the specified cell style.
\documentclass{article}

    
    
    \usepackage{graphicx} % Used to insert images
    \usepackage{adjustbox} % Used to constrain images to a maximum size 
    \usepackage{color} % Allow colors to be defined
    \usepackage{enumerate} % Needed for markdown enumerations to work
    \usepackage{geometry} % Used to adjust the document margins
    \usepackage{amsmath} % Equations
    \usepackage{amssymb} % Equations
    \usepackage{eurosym} % defines \euro
    \usepackage[mathletters]{ucs} % Extended unicode (utf-8) support
    \usepackage[utf8x]{inputenc} % Allow utf-8 characters in the tex document
    \usepackage{fancyvrb} % verbatim replacement that allows latex
    \usepackage{grffile} % extends the file name processing of package graphics 
                         % to support a larger range 
    % The hyperref package gives us a pdf with properly built
    % internal navigation ('pdf bookmarks' for the table of contents,
    % internal cross-reference links, web links for URLs, etc.)
    \usepackage[backref=page]{hyperref}

    \usepackage{longtable} % longtable support required by pandoc >1.10
    \usepackage{booktabs}  % table support for pandoc > 1.12.2
    

    
    
    \definecolor{orange}{cmyk}{0,0.4,0.8,0.2}
    \definecolor{darkorange}{rgb}{.71,0.21,0.01}
    \definecolor{darkgreen}{rgb}{.12,.54,.11}
    \definecolor{myteal}{rgb}{.26, .44, .56}
    \definecolor{gray}{gray}{0.45}
    \definecolor{lightgray}{gray}{.95}
    \definecolor{mediumgray}{gray}{.8}
    \definecolor{inputbackground}{rgb}{.95, .95, .85}
    \definecolor{outputbackground}{rgb}{.95, .95, .95}
    \definecolor{traceback}{rgb}{1, .95, .95}
    % ansi colors
    \definecolor{red}{rgb}{.6,0,0}
    \definecolor{green}{rgb}{0,.65,0}
    \definecolor{brown}{rgb}{0.6,0.6,0}
    \definecolor{blue}{rgb}{0,.145,.698}
    \definecolor{purple}{rgb}{.698,.145,.698}
    \definecolor{cyan}{rgb}{0,.698,.698}
    \definecolor{lightgray}{gray}{0.5}
    
    % bright ansi colors
    \definecolor{darkgray}{gray}{0.25}
    \definecolor{lightred}{rgb}{1.0,0.39,0.28}
    \definecolor{lightgreen}{rgb}{0.48,0.99,0.0}
    \definecolor{lightblue}{rgb}{0.53,0.81,0.92}
    \definecolor{lightpurple}{rgb}{0.87,0.63,0.87}
    \definecolor{lightcyan}{rgb}{0.5,1.0,0.83}
    
    % commands and environments needed by pandoc snippets
    % extracted from the output of `pandoc -s`
    \providecommand{\tightlist}{%
      \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
    \DefineVerbatimEnvironment{Highlighting}{Verbatim}{commandchars=\\\{\}}
    % Add ',fontsize=\small' for more characters per line
    \newenvironment{Shaded}{}{}
    \newcommand{\KeywordTok}[1]{\textcolor[rgb]{0.00,0.44,0.13}{\textbf{{#1}}}}
    \newcommand{\DataTypeTok}[1]{\textcolor[rgb]{0.56,0.13,0.00}{{#1}}}
    \newcommand{\DecValTok}[1]{\textcolor[rgb]{0.25,0.63,0.44}{{#1}}}
    \newcommand{\BaseNTok}[1]{\textcolor[rgb]{0.25,0.63,0.44}{{#1}}}
    \newcommand{\FloatTok}[1]{\textcolor[rgb]{0.25,0.63,0.44}{{#1}}}
    \newcommand{\CharTok}[1]{\textcolor[rgb]{0.25,0.44,0.63}{{#1}}}
    \newcommand{\StringTok}[1]{\textcolor[rgb]{0.25,0.44,0.63}{{#1}}}
    \newcommand{\CommentTok}[1]{\textcolor[rgb]{0.38,0.63,0.69}{\textit{{#1}}}}
    \newcommand{\OtherTok}[1]{\textcolor[rgb]{0.00,0.44,0.13}{{#1}}}
    \newcommand{\AlertTok}[1]{\textcolor[rgb]{1.00,0.00,0.00}{\textbf{{#1}}}}
    \newcommand{\FunctionTok}[1]{\textcolor[rgb]{0.02,0.16,0.49}{{#1}}}
    \newcommand{\RegionMarkerTok}[1]{{#1}}
    \newcommand{\ErrorTok}[1]{\textcolor[rgb]{1.00,0.00,0.00}{\textbf{{#1}}}}
    \newcommand{\NormalTok}[1]{{#1}}
    
    % Define a nice break command that doesn't care if a line doesn't already
    % exist.
    \def\br{\hspace*{\fill} \\* }
    % Math Jax compatability definitions
    \def\gt{>}
    \def\lt{<}
    % Document parameters
    
\title{Exploring the Stroop Effect utilizing IPython}

    
    
\author{Yigal Weinstein}

    

    % Pygments definitions
    
\makeatletter
\def\PY@reset{\let\PY@it=\relax \let\PY@bf=\relax%
    \let\PY@ul=\relax \let\PY@tc=\relax%
    \let\PY@bc=\relax \let\PY@ff=\relax}
\def\PY@tok#1{\csname PY@tok@#1\endcsname}
\def\PY@toks#1+{\ifx\relax#1\empty\else%
    \PY@tok{#1}\expandafter\PY@toks\fi}
\def\PY@do#1{\PY@bc{\PY@tc{\PY@ul{%
    \PY@it{\PY@bf{\PY@ff{#1}}}}}}}
\def\PY#1#2{\PY@reset\PY@toks#1+\relax+\PY@do{#2}}

\expandafter\def\csname PY@tok@si\endcsname{\let\PY@bf=\textbf\def\PY@tc##1{\textcolor[rgb]{0.73,0.40,0.53}{##1}}}
\expandafter\def\csname PY@tok@cp\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.74,0.48,0.00}{##1}}}
\expandafter\def\csname PY@tok@mo\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.40,0.40,0.40}{##1}}}
\expandafter\def\csname PY@tok@kt\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.69,0.00,0.25}{##1}}}
\expandafter\def\csname PY@tok@kp\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.00,0.50,0.00}{##1}}}
\expandafter\def\csname PY@tok@nn\endcsname{\let\PY@bf=\textbf\def\PY@tc##1{\textcolor[rgb]{0.00,0.00,1.00}{##1}}}
\expandafter\def\csname PY@tok@gd\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.63,0.00,0.00}{##1}}}
\expandafter\def\csname PY@tok@bp\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.00,0.50,0.00}{##1}}}
\expandafter\def\csname PY@tok@vi\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.10,0.09,0.49}{##1}}}
\expandafter\def\csname PY@tok@nc\endcsname{\let\PY@bf=\textbf\def\PY@tc##1{\textcolor[rgb]{0.00,0.00,1.00}{##1}}}
\expandafter\def\csname PY@tok@m\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.40,0.40,0.40}{##1}}}
\expandafter\def\csname PY@tok@nt\endcsname{\let\PY@bf=\textbf\def\PY@tc##1{\textcolor[rgb]{0.00,0.50,0.00}{##1}}}
\expandafter\def\csname PY@tok@gp\endcsname{\let\PY@bf=\textbf\def\PY@tc##1{\textcolor[rgb]{0.00,0.00,0.50}{##1}}}
\expandafter\def\csname PY@tok@cm\endcsname{\let\PY@it=\textit\def\PY@tc##1{\textcolor[rgb]{0.25,0.50,0.50}{##1}}}
\expandafter\def\csname PY@tok@ss\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.10,0.09,0.49}{##1}}}
\expandafter\def\csname PY@tok@gt\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.00,0.27,0.87}{##1}}}
\expandafter\def\csname PY@tok@il\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.40,0.40,0.40}{##1}}}
\expandafter\def\csname PY@tok@nf\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.00,0.00,1.00}{##1}}}
\expandafter\def\csname PY@tok@ge\endcsname{\let\PY@it=\textit}
\expandafter\def\csname PY@tok@err\endcsname{\def\PY@bc##1{\setlength{\fboxsep}{0pt}\fcolorbox[rgb]{1.00,0.00,0.00}{1,1,1}{\strut ##1}}}
\expandafter\def\csname PY@tok@kc\endcsname{\let\PY@bf=\textbf\def\PY@tc##1{\textcolor[rgb]{0.00,0.50,0.00}{##1}}}
\expandafter\def\csname PY@tok@gr\endcsname{\def\PY@tc##1{\textcolor[rgb]{1.00,0.00,0.00}{##1}}}
\expandafter\def\csname PY@tok@ni\endcsname{\let\PY@bf=\textbf\def\PY@tc##1{\textcolor[rgb]{0.60,0.60,0.60}{##1}}}
\expandafter\def\csname PY@tok@sb\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.73,0.13,0.13}{##1}}}
\expandafter\def\csname PY@tok@go\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.53,0.53,0.53}{##1}}}
\expandafter\def\csname PY@tok@sx\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.00,0.50,0.00}{##1}}}
\expandafter\def\csname PY@tok@nd\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.67,0.13,1.00}{##1}}}
\expandafter\def\csname PY@tok@sh\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.73,0.13,0.13}{##1}}}
\expandafter\def\csname PY@tok@c\endcsname{\let\PY@it=\textit\def\PY@tc##1{\textcolor[rgb]{0.25,0.50,0.50}{##1}}}
\expandafter\def\csname PY@tok@mh\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.40,0.40,0.40}{##1}}}
\expandafter\def\csname PY@tok@gh\endcsname{\let\PY@bf=\textbf\def\PY@tc##1{\textcolor[rgb]{0.00,0.00,0.50}{##1}}}
\expandafter\def\csname PY@tok@kn\endcsname{\let\PY@bf=\textbf\def\PY@tc##1{\textcolor[rgb]{0.00,0.50,0.00}{##1}}}
\expandafter\def\csname PY@tok@mi\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.40,0.40,0.40}{##1}}}
\expandafter\def\csname PY@tok@k\endcsname{\let\PY@bf=\textbf\def\PY@tc##1{\textcolor[rgb]{0.00,0.50,0.00}{##1}}}
\expandafter\def\csname PY@tok@vg\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.10,0.09,0.49}{##1}}}
\expandafter\def\csname PY@tok@s1\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.73,0.13,0.13}{##1}}}
\expandafter\def\csname PY@tok@gs\endcsname{\let\PY@bf=\textbf}
\expandafter\def\csname PY@tok@nl\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.63,0.63,0.00}{##1}}}
\expandafter\def\csname PY@tok@sd\endcsname{\let\PY@it=\textit\def\PY@tc##1{\textcolor[rgb]{0.73,0.13,0.13}{##1}}}
\expandafter\def\csname PY@tok@w\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.73,0.73,0.73}{##1}}}
\expandafter\def\csname PY@tok@s\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.73,0.13,0.13}{##1}}}
\expandafter\def\csname PY@tok@c1\endcsname{\let\PY@it=\textit\def\PY@tc##1{\textcolor[rgb]{0.25,0.50,0.50}{##1}}}
\expandafter\def\csname PY@tok@no\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.53,0.00,0.00}{##1}}}
\expandafter\def\csname PY@tok@o\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.40,0.40,0.40}{##1}}}
\expandafter\def\csname PY@tok@s2\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.73,0.13,0.13}{##1}}}
\expandafter\def\csname PY@tok@gi\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.00,0.63,0.00}{##1}}}
\expandafter\def\csname PY@tok@mb\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.40,0.40,0.40}{##1}}}
\expandafter\def\csname PY@tok@nb\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.00,0.50,0.00}{##1}}}
\expandafter\def\csname PY@tok@nv\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.10,0.09,0.49}{##1}}}
\expandafter\def\csname PY@tok@na\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.49,0.56,0.16}{##1}}}
\expandafter\def\csname PY@tok@kr\endcsname{\let\PY@bf=\textbf\def\PY@tc##1{\textcolor[rgb]{0.00,0.50,0.00}{##1}}}
\expandafter\def\csname PY@tok@ne\endcsname{\let\PY@bf=\textbf\def\PY@tc##1{\textcolor[rgb]{0.82,0.25,0.23}{##1}}}
\expandafter\def\csname PY@tok@sr\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.73,0.40,0.53}{##1}}}
\expandafter\def\csname PY@tok@kd\endcsname{\let\PY@bf=\textbf\def\PY@tc##1{\textcolor[rgb]{0.00,0.50,0.00}{##1}}}
\expandafter\def\csname PY@tok@cs\endcsname{\let\PY@it=\textit\def\PY@tc##1{\textcolor[rgb]{0.25,0.50,0.50}{##1}}}
\expandafter\def\csname PY@tok@mf\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.40,0.40,0.40}{##1}}}
\expandafter\def\csname PY@tok@se\endcsname{\let\PY@bf=\textbf\def\PY@tc##1{\textcolor[rgb]{0.73,0.40,0.13}{##1}}}
\expandafter\def\csname PY@tok@gu\endcsname{\let\PY@bf=\textbf\def\PY@tc##1{\textcolor[rgb]{0.50,0.00,0.50}{##1}}}
\expandafter\def\csname PY@tok@ow\endcsname{\let\PY@bf=\textbf\def\PY@tc##1{\textcolor[rgb]{0.67,0.13,1.00}{##1}}}
\expandafter\def\csname PY@tok@sc\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.73,0.13,0.13}{##1}}}
\expandafter\def\csname PY@tok@vc\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.10,0.09,0.49}{##1}}}

\def\PYZbs{\char`\\}
\def\PYZus{\char`\_}
\def\PYZob{\char`\{}
\def\PYZcb{\char`\}}
\def\PYZca{\char`\^}
\def\PYZam{\char`\&}
\def\PYZlt{\char`\<}
\def\PYZgt{\char`\>}
\def\PYZsh{\char`\#}
\def\PYZpc{\char`\%}
\def\PYZdl{\char`\$}
\def\PYZhy{\char`\-}
\def\PYZsq{\char`\'}
\def\PYZdq{\char`\"}
\def\PYZti{\char`\~}
% for compatibility with earlier versions
\def\PYZat{@}
\def\PYZlb{[}
\def\PYZrb{]}
\makeatother


    % Exact colors from NB
    \definecolor{incolor}{rgb}{0.0, 0.0, 0.5}
    \definecolor{outcolor}{rgb}{0.545, 0.0, 0.0}



    
    % Prevent overflowing lines due to hard-to-break entities
    \sloppy 
    % Setup hyperref package
    \hypersetup{
      breaklinks=true,  % so long urls are correctly broken across lines
      colorlinks=true,
      urlcolor=blue,
      linkcolor=darkorange,
      citecolor=darkgreen,
      }
    % Slightly bigger margins than the latex defaults
    
    \geometry{verbose,tmargin=1in,bmargin=1in,lmargin=1in,rmargin=1in}
    
    

    \begin{document}
    
    
    \maketitle
    
    

    
    ** Introduction **

In a Stroop task, participants are presented with a list of words, with
each word displayed in a color of ink. The participant's task is to say
out loud the color of the ink in which the word is printed. The task has
two conditions: a congruent words condition, and an incongruent words
condition. In the congruent words condition, the words being displayed
are color words whose names match the colors in which they are printed:
for example RED, BLUE. In the incongruent words condition, the words
displayed are color words whose names do not match the colors in which
they are printed: for example PURPLE, ORANGE. In each case, we measure
the time it takes to name the ink colors in equally-sized lists. Each
participant will go through and record a time from each condition.
Questions For Investigation\cite{Udacity-P1-Stroop}

As a general note, be sure to keep a record of any resources that you
use or refer to in the creation of your project. You will need to report
your sources as part of the project submission.

    \begin{Verbatim}[commandchars=\\\{\}]
{\color{incolor}In [{\color{incolor} }]:} \PY{k+kn}{from} \PY{n+nn}{sympy}\PY{n+nn}{.}\PY{n+nn}{interactive} \PY{k}{import} \PY{n}{printing}
        \PY{n}{printing}\PY{o}{.}\PY{n}{init\PYZus{}printing}\PY{p}{(}\PY{n}{use\PYZus{}latex}\PY{o}{=}\PY{k}{True}\PY{p}{)}
\end{Verbatim}

\section{What is our independent variable? What is our dependent
variable?}\label{what-is-our-independent-variable-what-is-our-dependent-variable}

The independent variable is a binary condition that of either congruency
or incongruency between the color of a word, and the symantic meaning of
the word. As example the word `RED' is a congruent example where the
word `red' has the color of its symantic meaning, i.e.~the color it
represents, and `BLUE' is an incongruent case where the word `blue'
which has the symantic meaning of the color blue is instead the color
green. Frome here on out the terms congruent color selection, CCS, and
incongruent color selection, ICS, will be used to denote the two
conditions the dependent variable may take that of a word representing a
color being colored with or with a different color respectively.

The dependent variable is the time, in seconds, it takes to read through
an equal sized lists of CCS or ICS words.

\section{What is an appropriate set of hypotheses for this task? What
kind of statistical test do you expect to perform? Justify your
choices.}\label{what-is-an-appropriate-set-of-hypotheses-for-this-task-what-kind-of-statistical-test-do-you-expect-to-perform-justify-your-choices.}

The null hypothesis, \(H_0\) is the statement that the ICS task will
take less or an equal amount of time to the CCS task. The alternative
hypothesis, \(H_A\) is the statement that the mean population time to
read an ICS list will be greater than an equally sized CCS list. The
null and alternative hypothesis choice stems from a need to test
quantatively the validity and extent of an already well respected
phenomenon the Stroop effect. The Stroop effect being defined to mean
that cognitive incongruences will lead to an increase in the reaction
time of a task.\\ It is true that this single tailed objective may not
provide insight if indeed the reaction time for ICS word lists take, on
the average, less time to complete, however this is a test regarding the
scope and veracity of the Stroop effect which has been shown in many
previous quantative tests to have general validity. If indeed the ICS
task takes less time it is enough that \(H_0\) should be kept to cause
doubt regarding the validity of either the test or the Stroop effect.
That is due to the large body of work already done to test the effect if
\(H_0\) is kept there is either something wrong with the experiment or
the Stroop effect has either more limitations on generalizability than
expected or there are indeed real issues with it's veracity. So to sum
things up via a set of equations:

\begin{align}
H_0:\; \mu_{ICS} &&\le&& \mu_{CCS} \\
H_A:\; \mu_{ICS} &&>&& \mu_{CCS}
\end{align}

\section{Report some descriptive statistics regarding this dataset.
Include at least one measure of central tendency and at least one
measure of
variability.}\label{report-some-descriptive-statistics-regarding-this-dataset.-include-at-least-one-measure-of-central-tendency-and-at-least-one-measure-of-variability.}

Below I've printed the mean, sample standard deviation, minimum values,
25th, 50th, 75th percentiles, maximums, and the median for both the CCS
and ICS samples, all values are in seconds. For central tendency I've
included both the mean, and the median - which in this case is simply
the 50th percentile. Notice the fact that for both CCS and ICS the
median and mean are nearly identical, for the CCS case it's less than
one third of a second difference, and for the ICS case the difference
between these two measure of central tendency is only slightly greater
than a second. This points to both distribution being evenly distributed
around the mean. As we can see for nearly all percentiles, minimum and
maximum, and mean values the CCS times are roughly two thirds of the
value of the ICS times, and all times for every category are
significantly longer for the ICS sample relative to the CCS.

An indication of the relative spread can be observed by looking at the
sample standard deviations. the ICS case is slightly more spread out
than the CCS case \(4.797s\) to \(3.559s\) respectively, i.e slightly
over a second more for the ICS sample. To gain a better descriptive
understanding of the spread we can also look at the range, i.e.
\(R = x_{max} - x_{min}\) of the two samples:

\begin{align}
R_{CCS} &= 22.328000 - 8.630000 & = 13.698\\
R_{ICS} &= 35.255000 - 15.687000 & = 19.568
\end{align}

From both the sample standard deviation and the range we can see that
the spread of the ICS sample is greater both in terms of the range,
i.e.~outliers, and of the sample standard deviation:

    \begin{Verbatim}[commandchars=\\\{\}]
{\color{incolor}In [{\color{incolor} }]:} \PY{k+kn}{import} \PY{n+nn}{pandas} \PY{k}{as} \PY{n+nn}{pd}
        \PY{k+kn}{import} \PY{n+nn}{numpy} \PY{k}{as} \PY{n+nn}{np}
        \PY{n}{stroopdata} \PY{o}{=} \PY{n}{pd}\PY{o}{.}\PY{n}{read\PYZus{}csv}\PY{p}{(}\PY{l+s}{\PYZsq{}}\PY{l+s}{stroopdata.csv}\PY{l+s}{\PYZsq{}}\PY{p}{)}
        \PY{n}{stroopdata}\PY{o}{.}\PY{n}{describe}\PY{p}{(}\PY{p}{)}
\end{Verbatim}

    and a simple calculation of the range for the CCS and ICS samples:

    \begin{Verbatim}[commandchars=\\\{\}]
{\color{incolor}In [{\color{incolor} }]:} \PY{n+nb}{print}\PY{p}{(}\PY{l+s}{\PYZdq{}}\PY{l+s+se}{\PYZbs{}n}\PY{l+s}{The range for the two cases:}\PY{l+s+se}{\PYZbs{}n}\PY{l+s}{\PYZdq{}}\PY{p}{,} \PY{n}{stroopdata}\PY{o}{.}\PY{n}{max}\PY{p}{(}\PY{p}{)} \PY{o}{\PYZhy{}} \PY{n}{stroopdata}\PY{o}{.}\PY{n}{min}\PY{p}{(}\PY{p}{)}\PY{p}{)}
\end{Verbatim}

    \section{Provide one or two visualizations that show the distribution of
the sample data. Write one or two sentences noting what you observe
about the plot or
plots.}\label{provide-one-or-two-visualizations-that-show-the-distribution-of-the-sample-data.-write-one-or-two-sentences-noting-what-you-observe-about-the-plot-or-plots.}

    

    \begin{Verbatim}[commandchars=\\\{\}]
{\color{incolor}In [{\color{incolor} }]:} \PY{k+kn}{import} \PY{n+nn}{numpy} \PY{k}{as} \PY{n+nn}{np}
        \PY{k+kn}{import} \PY{n+nn}{matplotlib}\PY{n+nn}{.}\PY{n+nn}{pyplot} \PY{k}{as} \PY{n+nn}{plt}
        
        \PY{o}{\PYZpc{}}\PY{k}{pylab} inline
        \PY{n}{pylab}\PY{o}{.}\PY{n}{rcParams}\PY{p}{[}\PY{l+s}{\PYZsq{}}\PY{l+s}{figure.figsize}\PY{l+s}{\PYZsq{}}\PY{p}{]} \PY{o}{=} \PY{p}{(}\PY{l+m+mf}{8.0}\PY{p}{,} \PY{l+m+mf}{7.0}\PY{p}{)}
        
        \PY{n}{fig}\PY{p}{,} \PY{n}{ax} \PY{o}{=} \PY{n}{plt}\PY{o}{.}\PY{n}{subplots}\PY{p}{(}\PY{p}{)}
        
        \PY{n}{index} \PY{o}{=} \PY{n}{np}\PY{o}{.}\PY{n}{arange}\PY{p}{(}\PY{n}{stroopdata}\PY{o}{.}\PY{n}{shape}\PY{p}{[}\PY{l+m+mi}{0}\PY{p}{]}\PY{p}{)}
        \PY{n}{bar\PYZus{}width} \PY{o}{=} \PY{l+m+mf}{0.35}
        
        \PY{c}{\PYZsh{}opacity = 0.6}
        
        \PY{n}{rects1} \PY{o}{=} \PY{n}{plt}\PY{o}{.}\PY{n}{bar}\PY{p}{(}\PY{n}{index}\PY{p}{,} \PY{n}{stroopdata}\PY{p}{[}\PY{l+s}{\PYZsq{}}\PY{l+s}{Congruent}\PY{l+s}{\PYZsq{}}\PY{p}{]}\PY{p}{,} 
                         \PY{n}{bar\PYZus{}width}\PY{p}{,}
                         \PY{n}{alpha}\PY{o}{=}\PY{n}{opacity}\PY{p}{,}
                         \PY{n}{color}\PY{o}{=}\PY{l+s}{\PYZsq{}}\PY{l+s}{k}\PY{l+s}{\PYZsq{}}\PY{p}{,}
                         \PY{n}{label}\PY{o}{=}\PY{l+s}{\PYZsq{}}\PY{l+s}{CCS Sample}\PY{l+s}{\PYZsq{}}\PY{p}{)}
        
        \PY{n}{rects2} \PY{o}{=} \PY{n}{plt}\PY{o}{.}\PY{n}{bar}\PY{p}{(}\PY{n}{index} \PY{o}{+} \PY{n}{bar\PYZus{}width}\PY{p}{,} \PY{n}{stroopdata}\PY{p}{[}\PY{l+s}{\PYZsq{}}\PY{l+s}{Incongruent}\PY{l+s}{\PYZsq{}}\PY{p}{]}\PY{p}{,} 
                         \PY{n}{bar\PYZus{}width}\PY{p}{,}
                         \PY{n}{alpha}\PY{o}{=}\PY{n}{opacity}\PY{p}{,}
                         \PY{n}{color}\PY{o}{=}\PY{l+s}{\PYZsq{}}\PY{l+s}{b}\PY{l+s}{\PYZsq{}}\PY{p}{,}
                         \PY{n}{label}\PY{o}{=}\PY{l+s}{\PYZsq{}}\PY{l+s}{ICS Sample}\PY{l+s}{\PYZsq{}}\PY{p}{)}
        
        \PY{c}{\PYZsh{} add some text for labels, title and axes ticks}
        \PY{n}{plt}\PY{o}{.}\PY{n}{xlabel}\PY{p}{(}\PY{l+s}{\PYZsq{}}\PY{l+s}{Subject \PYZsh{}}\PY{l+s}{\PYZsq{}}\PY{p}{)}
        \PY{n}{plt}\PY{o}{.}\PY{n}{ylabel}\PY{p}{(}\PY{l+s}{\PYZsq{}}\PY{l+s}{Time (s)}\PY{l+s}{\PYZsq{}}\PY{p}{)}
        \PY{n}{plt}\PY{o}{.}\PY{n}{title}\PY{p}{(}\PY{l+s}{\PYZsq{}}\PY{l+s}{Scores for CCS and ICS}\PY{l+s}{\PYZsq{}}\PY{p}{)}
        \PY{n}{plt}\PY{o}{.}\PY{n}{xticks}\PY{p}{(}\PY{n}{index} \PY{o}{+} \PY{n}{bar\PYZus{}width}\PY{p}{,} \PY{n+nb}{range}\PY{p}{(}\PY{l+m+mi}{1}\PY{p}{,}\PY{l+m+mi}{25}\PY{p}{)}\PY{p}{)}
        \PY{n}{plt}\PY{o}{.}\PY{n}{legend}\PY{p}{(}\PY{p}{)}
        
        \PY{n}{plt}\PY{o}{.}\PY{n}{tight\PYZus{}layout}\PY{p}{(}\PY{p}{)}
        \PY{n}{plt}\PY{o}{.}\PY{n}{show}\PY{p}{(}\PY{p}{)}
\end{Verbatim}

    The bar graph above shows graphically that each subject took more time
on the ICS word list than on the CCS word list.

    \section{Now, perform the statistical test and report your results. What
is your confidence level and your critical statistic value? Do you
reject the null hypothesis or fail to reject it? Come to a conclusion in
terms of the experiment task. Did the results match up with your
expectations?}\label{now-perform-the-statistical-test-and-report-your-results.-what-is-your-confidence-level-and-your-critical-statistic-value-do-you-reject-the-null-hypothesis-or-fail-to-reject-it-come-to-a-conclusion-in-terms-of-the-experiment-task.-did-the-results-match-up-with-your-expectations}

\section{What do you think is responsible for the effects observed? Can
you think of an alternative or similar task that would result in a
similar effect? Some research about the problem will be helpful for
thinking about these two
questions!}\label{what-do-you-think-is-responsible-for-the-effects-observed-can-you-think-of-an-alternative-or-similar-task-that-would-result-in-a-similar-effect-some-research-about-the-problem-will-be-helpful-for-thinking-about-these-two-questions}

    \paragraph{Refrences:}\label{refrences}

http://pandas.pydata.org/pandas-docs/stable/io.html\#io-read-csv-table
\# link for reading in CSV file

https://docs.google.com/document/d/1-OkpZLjG\_kX9J6LIQ5IltsqMzVWjh36QpnP2RYpVdPU/pub
\# Udacity official document on general instructions for further
projects as well as specifically for the Stroop Effect, P1.

https://docs.google.com/document/d/1bqyi1Fm5truesLhmbAq16Zl-Ajj9bnNIU\_68P60nDQg/pub
\# Udacity official documentation outlining what is expected to
satisfactorily complete a project

http://matplotlib.org/examples/api/barchart\_demo.html \# The bar graph
example was used as a basis for the bar graph in this report.

http://matplotlib.org/api/colors\_api.html \# understanding colors in
matplotlib

    \begin{Verbatim}[commandchars=\\\{\}]
{\color{incolor}In [{\color{incolor}1}]:} \PY{o}{\PYZpc{}\PYZpc{}}\PY{k}{bash}
        ipython3 nbconvert \PYZhy{}\PYZhy{}template udacity.tplx  \PYZhy{}\PYZhy{}to latex \PYZdq{}Stroop Effect.ipynb\PYZdq{}
        pdflatex \PYZdq{}Stroop Effect\PYZdq{}
        bibtex \PYZdq{}Stroop Effect\PYZdq{}
        pdflatex \PYZdq{}Stroop Effect\PYZdq{}
\end{Verbatim}

    \begin{Verbatim}[commandchars=\\\{\}]
This is pdfTeX, Version 3.14159265-2.6-1.40.16 (TeX Live 2015) (preloaded format=pdflatex)
 restricted \textbackslash{}write18 enabled.
entering extended mode
(./Stroop Effect.tex
LaTeX2e <2015/01/01> patch level 2
Babel <3.9m> and hyphenation patterns for 79 languages loaded.
(/home/yigal/.texlive/2015/texmf-dist/tex/latex/base/article.cls
Document Class: article 2014/09/29 v1.4h Standard LaTeX document class
(/home/yigal/.texlive/2015/texmf-dist/tex/latex/base/size10.clo))
(/home/yigal/.texlive/2015/texmf-dist/tex/latex/graphics/graphicx.sty
(/home/yigal/.texlive/2015/texmf-dist/tex/latex/graphics/keyval.sty)
(/home/yigal/.texlive/2015/texmf-dist/tex/latex/graphics/graphics.sty
(/home/yigal/.texlive/2015/texmf-dist/tex/latex/graphics/trig.sty)
(/home/yigal/.texlive/2015/texmf-dist/tex/latex/latexconfig/graphics.cfg)
(/home/yigal/.texlive/2015/texmf-dist/tex/latex/pdftex-def/pdftex.def
(/home/yigal/.texlive/2015/texmf-dist/tex/generic/oberdiek/infwarerr.sty)
(/home/yigal/.texlive/2015/texmf-dist/tex/generic/oberdiek/ltxcmds.sty))))
(/home/yigal/.texlive/2015/texmf-dist/tex/latex/adjustbox/adjustbox.sty
(/home/yigal/.texlive/2015/texmf-dist/tex/latex/xkeyval/xkeyval.sty
(/home/yigal/.texlive/2015/texmf-dist/tex/generic/xkeyval/xkeyval.tex
(/home/yigal/.texlive/2015/texmf-dist/tex/generic/xkeyval/xkvutils.tex)))
(/home/yigal/.texlive/2015/texmf-dist/tex/latex/adjustbox/adjcalc.sty)
(/home/yigal/.texlive/2015/texmf-dist/tex/latex/adjustbox/trimclip.sty
(/home/yigal/.texlive/2015/texmf-dist/tex/latex/collectbox/collectbox.sty)
(/home/yigal/.texlive/2015/texmf-dist/tex/latex/adjustbox/tc-pdftex.def))
(/home/yigal/.texlive/2015/texmf-dist/tex/latex/ifoddpage/ifoddpage.sty)
(/home/yigal/.texlive/2015/texmf-dist/tex/latex/varwidth/varwidth.sty))
(/home/yigal/.texlive/2015/texmf-dist/tex/latex/graphics/color.sty
(/home/yigal/.texlive/2015/texmf-dist/tex/latex/latexconfig/color.cfg))
(/home/yigal/.texlive/2015/texmf-dist/tex/latex/tools/enumerate.sty)
(/home/yigal/.texlive/2015/texmf-dist/tex/latex/geometry/geometry.sty
(/home/yigal/.texlive/2015/texmf-dist/tex/generic/oberdiek/ifpdf.sty)
(/home/yigal/.texlive/2015/texmf-dist/tex/generic/oberdiek/ifvtex.sty)
(/home/yigal/.texlive/2015/texmf-dist/tex/generic/ifxetex/ifxetex.sty))
(/home/yigal/.texlive/2015/texmf-dist/tex/latex/amsmath/amsmath.sty
For additional information on amsmath, use the `?' option.
(/home/yigal/.texlive/2015/texmf-dist/tex/latex/amsmath/amstext.sty
(/home/yigal/.texlive/2015/texmf-dist/tex/latex/amsmath/amsgen.sty))
(/home/yigal/.texlive/2015/texmf-dist/tex/latex/amsmath/amsbsy.sty)
(/home/yigal/.texlive/2015/texmf-dist/tex/latex/amsmath/amsopn.sty))
(/home/yigal/.texlive/2015/texmf-dist/tex/latex/amsfonts/amssymb.sty
(/home/yigal/.texlive/2015/texmf-dist/tex/latex/amsfonts/amsfonts.sty))
(/home/yigal/.texlive/2015/texmf-dist/tex/latex/eurosym/eurosym.sty)
(/home/yigal/.texlive/2015/texmf-dist/tex/latex/ucs/ucs.sty
(/home/yigal/.texlive/2015/texmf-dist/tex/latex/ucs/data/uni-global.def))
(/home/yigal/.texlive/2015/texmf-dist/tex/latex/base/inputenc.sty
(/home/yigal/.texlive/2015/texmf-dist/tex/latex/ucs/utf8x.def))
(/home/yigal/.texlive/2015/texmf-dist/tex/latex/fancyvrb/fancyvrb.sty
Style option: `fancyvrb' v2.7a, with DG/SPQR fixes, and firstline=lastline fix 
<2008/02/07> (tvz))
(/home/yigal/.texlive/2015/texmf-dist/tex/latex/oberdiek/grffile.sty
(/home/yigal/.texlive/2015/texmf-dist/tex/latex/oberdiek/kvoptions.sty
(/home/yigal/.texlive/2015/texmf-dist/tex/generic/oberdiek/kvsetkeys.sty
(/home/yigal/.texlive/2015/texmf-dist/tex/generic/oberdiek/etexcmds.sty
(/home/yigal/.texlive/2015/texmf-dist/tex/generic/oberdiek/ifluatex.sty))))
(/home/yigal/.texlive/2015/texmf-dist/tex/generic/oberdiek/pdftexcmds.sty))
(/home/yigal/.texlive/2015/texmf-dist/tex/latex/hyperref/hyperref.sty
(/home/yigal/.texlive/2015/texmf-dist/tex/generic/oberdiek/hobsub-hyperref.sty
(/home/yigal/.texlive/2015/texmf-dist/tex/generic/oberdiek/hobsub-generic.sty))
 (/home/yigal/.texlive/2015/texmf-dist/tex/latex/oberdiek/auxhook.sty)
(/home/yigal/.texlive/2015/texmf-dist/tex/latex/hyperref/pd1enc.def)
(/home/yigal/.texlive/2015/texmf-dist/tex/latex/latexconfig/hyperref.cfg)
(/home/yigal/.texlive/2015/texmf-dist/tex/latex/url/url.sty))

Package hyperref Message: Driver (autodetected): hpdftex.

(/home/yigal/.texlive/2015/texmf-dist/tex/latex/hyperref/hpdftex.def
(/home/yigal/.texlive/2015/texmf-dist/tex/latex/oberdiek/rerunfilecheck.sty))
(/home/yigal/.texlive/2015/texmf-dist/tex/latex/tools/longtable.sty)
(/home/yigal/.texlive/2015/texmf-dist/tex/latex/booktabs/booktabs.sty)
(./Stroop Effect.aux)
(/home/yigal/.texlive/2015/texmf-dist/tex/context/base/supp-pdf.mkii
[Loading MPS to PDF converter (version 2006.09.02).]
) (/home/yigal/.texlive/2015/texmf-dist/tex/latex/oberdiek/epstopdf-base.sty
(/home/yigal/.texlive/2015/texmf-dist/tex/latex/oberdiek/grfext.sty)
(/home/yigal/.texlive/2015/texmf-dist/tex/latex/latexconfig/epstopdf-sys.cfg))
*geometry* driver: auto-detecting
*geometry* detected driver: pdftex

Package geometry Warning: The marginal notes overrun the paper.
     Add 3.73001pt and more to the right margin.

*geometry* verbose mode - [ preamble ] result:
* driver: pdftex
* paper: <default>
* layout: <same size as paper>
* layoutoffset:(h,v)=(0.0pt,0.0pt)
* modes: 
* h-part:(L,W,R)=(72.26999pt, 469.75502pt, 72.26999pt)
* v-part:(T,H,B)=(72.26999pt, 650.43001pt, 72.26999pt)
* \textbackslash{}paperwidth=614.295pt
* \textbackslash{}paperheight=794.96999pt
* \textbackslash{}textwidth=469.75502pt
* \textbackslash{}textheight=650.43001pt
* \textbackslash{}oddsidemargin=0.0pt
* \textbackslash{}evensidemargin=0.0pt
* \textbackslash{}topmargin=-37.0pt
* \textbackslash{}headheight=12.0pt
* \textbackslash{}headsep=25.0pt
* \textbackslash{}topskip=10.0pt
* \textbackslash{}footskip=30.0pt
* \textbackslash{}marginparwidth=65.0pt
* \textbackslash{}marginparsep=11.0pt
* \textbackslash{}columnsep=10.0pt
* \textbackslash{}skip\textbackslash{}footins=9.0pt plus 4.0pt minus 2.0pt
* \textbackslash{}hoffset=0.0pt
* \textbackslash{}voffset=0.0pt
* \textbackslash{}mag=1000
* \textbackslash{}@twocolumnfalse
* \textbackslash{}@twosidefalse
* \textbackslash{}@mparswitchfalse
* \textbackslash{}@reversemarginfalse
* (1in=72.27pt=25.4mm, 1cm=28.453pt)

(/home/yigal/.texlive/2015/texmf-dist/tex/latex/ucs/ucsencs.def)
(/home/yigal/.texlive/2015/texmf-dist/tex/latex/hyperref/nameref.sty
(/home/yigal/.texlive/2015/texmf-dist/tex/generic/oberdiek/gettitlestring.sty))
(./Stroop Effect.out) (./Stroop Effect.out)
(/home/yigal/.texlive/2015/texmf-dist/tex/latex/amsfonts/umsa.fd)
(/home/yigal/.texlive/2015/texmf-dist/tex/latex/amsfonts/umsb.fd)
(/home/yigal/.texlive/2015/texmf-dist/tex/latex/ucs/data/uni-32.def) [1\{/home/y
igal/.texlive/2015/texmf-var/fonts/map/pdftex/updmap/pdftex.map\}] [2] [3]
<Stroop Effect\_files/Stroop Effect\_9\_1.png, id=62, 571.13374pt x 499.8675pt>
<use Stroop Effect\_files/Stroop Effect\_9\_1.png>
Underfull \textbackslash{}hbox (badness 10000) in paragraph at lines 442--443

[4 <./Stroop Effect\_files/Stroop Effect\_9\_1.png>]
Underfull \textbackslash{}hbox (badness 10000) in paragraph at lines 468--471
[]\textbackslash{}OT1/cmr/m/n/10 https://docs.google.com/document/d/1bqyi1Fm5truesLhmbAq16Zl-A
jj9bnNIU[]68P60nDQg/pub \#

LaTeX Font Warning: Font shape `OMS/cmtt/m/n' undefined
(Font)              using `OMS/cmsy/m/n' instead
(Font)              for symbol `textbackslash' on input line 488.

[5] [6] [7] [8] [9] [10] [11] (./Stroop Effect.bbl) [12] (./Stroop Effect.aux)

LaTeX Font Warning: Some font shapes were not available, defaults substituted.

 )
(see the transcript file for additional information)</home/yigal/.texlive/2015/
texmf-dist/fonts/type1/public/amsfonts/cm/cmbx10.pfb></home/yigal/.texlive/2015
/texmf-dist/fonts/type1/public/amsfonts/cm/cmbx12.pfb></home/yigal/.texlive/201
5/texmf-dist/fonts/type1/public/amsfonts/cm/cmitt10.pfb></home/yigal/.texlive/2
015/texmf-dist/fonts/type1/public/amsfonts/cm/cmmi10.pfb></home/yigal/.texlive/
2015/texmf-dist/fonts/type1/public/amsfonts/cm/cmmi7.pfb></home/yigal/.texlive/
2015/texmf-dist/fonts/type1/public/amsfonts/cm/cmr10.pfb></home/yigal/.texlive/
2015/texmf-dist/fonts/type1/public/amsfonts/cm/cmr12.pfb></home/yigal/.texlive/
2015/texmf-dist/fonts/type1/public/amsfonts/cm/cmr17.pfb></home/yigal/.texlive/
2015/texmf-dist/fonts/type1/public/amsfonts/cm/cmr7.pfb></home/yigal/.texlive/2
015/texmf-dist/fonts/type1/public/amsfonts/cm/cmsy10.pfb></home/yigal/.texlive/
2015/texmf-dist/fonts/type1/public/amsfonts/cm/cmti10.pfb></home/yigal/.texlive
/2015/texmf-dist/fonts/type1/public/amsfonts/cm/cmtt10.pfb>
Output written on "Stroop Effect.pdf" (12 pages, 184279 bytes).
Transcript written on "Stroop Effect.log".
This is BibTeX, Version 0.99d (TeX Live 2015)
The top-level auxiliary file: Stroop Effect.aux
The style file: unsrt.bst
Database file \#1: udacity.bib
This is pdfTeX, Version 3.14159265-2.6-1.40.16 (TeX Live 2015) (preloaded format=pdflatex)
 restricted \textbackslash{}write18 enabled.
entering extended mode
(./Stroop Effect.tex
LaTeX2e <2015/01/01> patch level 2
Babel <3.9m> and hyphenation patterns for 79 languages loaded.
(/home/yigal/.texlive/2015/texmf-dist/tex/latex/base/article.cls
Document Class: article 2014/09/29 v1.4h Standard LaTeX document class
(/home/yigal/.texlive/2015/texmf-dist/tex/latex/base/size10.clo))
(/home/yigal/.texlive/2015/texmf-dist/tex/latex/graphics/graphicx.sty
(/home/yigal/.texlive/2015/texmf-dist/tex/latex/graphics/keyval.sty)
(/home/yigal/.texlive/2015/texmf-dist/tex/latex/graphics/graphics.sty
(/home/yigal/.texlive/2015/texmf-dist/tex/latex/graphics/trig.sty)
(/home/yigal/.texlive/2015/texmf-dist/tex/latex/latexconfig/graphics.cfg)
(/home/yigal/.texlive/2015/texmf-dist/tex/latex/pdftex-def/pdftex.def
(/home/yigal/.texlive/2015/texmf-dist/tex/generic/oberdiek/infwarerr.sty)
(/home/yigal/.texlive/2015/texmf-dist/tex/generic/oberdiek/ltxcmds.sty))))
(/home/yigal/.texlive/2015/texmf-dist/tex/latex/adjustbox/adjustbox.sty
(/home/yigal/.texlive/2015/texmf-dist/tex/latex/xkeyval/xkeyval.sty
(/home/yigal/.texlive/2015/texmf-dist/tex/generic/xkeyval/xkeyval.tex
(/home/yigal/.texlive/2015/texmf-dist/tex/generic/xkeyval/xkvutils.tex)))
(/home/yigal/.texlive/2015/texmf-dist/tex/latex/adjustbox/adjcalc.sty)
(/home/yigal/.texlive/2015/texmf-dist/tex/latex/adjustbox/trimclip.sty
(/home/yigal/.texlive/2015/texmf-dist/tex/latex/collectbox/collectbox.sty)
(/home/yigal/.texlive/2015/texmf-dist/tex/latex/adjustbox/tc-pdftex.def))
(/home/yigal/.texlive/2015/texmf-dist/tex/latex/ifoddpage/ifoddpage.sty)
(/home/yigal/.texlive/2015/texmf-dist/tex/latex/varwidth/varwidth.sty))
(/home/yigal/.texlive/2015/texmf-dist/tex/latex/graphics/color.sty
(/home/yigal/.texlive/2015/texmf-dist/tex/latex/latexconfig/color.cfg))
(/home/yigal/.texlive/2015/texmf-dist/tex/latex/tools/enumerate.sty)
(/home/yigal/.texlive/2015/texmf-dist/tex/latex/geometry/geometry.sty
(/home/yigal/.texlive/2015/texmf-dist/tex/generic/oberdiek/ifpdf.sty)
(/home/yigal/.texlive/2015/texmf-dist/tex/generic/oberdiek/ifvtex.sty)
(/home/yigal/.texlive/2015/texmf-dist/tex/generic/ifxetex/ifxetex.sty))
(/home/yigal/.texlive/2015/texmf-dist/tex/latex/amsmath/amsmath.sty
For additional information on amsmath, use the `?' option.
(/home/yigal/.texlive/2015/texmf-dist/tex/latex/amsmath/amstext.sty
(/home/yigal/.texlive/2015/texmf-dist/tex/latex/amsmath/amsgen.sty))
(/home/yigal/.texlive/2015/texmf-dist/tex/latex/amsmath/amsbsy.sty)
(/home/yigal/.texlive/2015/texmf-dist/tex/latex/amsmath/amsopn.sty))
(/home/yigal/.texlive/2015/texmf-dist/tex/latex/amsfonts/amssymb.sty
(/home/yigal/.texlive/2015/texmf-dist/tex/latex/amsfonts/amsfonts.sty))
(/home/yigal/.texlive/2015/texmf-dist/tex/latex/eurosym/eurosym.sty)
(/home/yigal/.texlive/2015/texmf-dist/tex/latex/ucs/ucs.sty
(/home/yigal/.texlive/2015/texmf-dist/tex/latex/ucs/data/uni-global.def))
(/home/yigal/.texlive/2015/texmf-dist/tex/latex/base/inputenc.sty
(/home/yigal/.texlive/2015/texmf-dist/tex/latex/ucs/utf8x.def))
(/home/yigal/.texlive/2015/texmf-dist/tex/latex/fancyvrb/fancyvrb.sty
Style option: `fancyvrb' v2.7a, with DG/SPQR fixes, and firstline=lastline fix 
<2008/02/07> (tvz))
(/home/yigal/.texlive/2015/texmf-dist/tex/latex/oberdiek/grffile.sty
(/home/yigal/.texlive/2015/texmf-dist/tex/latex/oberdiek/kvoptions.sty
(/home/yigal/.texlive/2015/texmf-dist/tex/generic/oberdiek/kvsetkeys.sty
(/home/yigal/.texlive/2015/texmf-dist/tex/generic/oberdiek/etexcmds.sty
(/home/yigal/.texlive/2015/texmf-dist/tex/generic/oberdiek/ifluatex.sty))))
(/home/yigal/.texlive/2015/texmf-dist/tex/generic/oberdiek/pdftexcmds.sty))
(/home/yigal/.texlive/2015/texmf-dist/tex/latex/hyperref/hyperref.sty
(/home/yigal/.texlive/2015/texmf-dist/tex/generic/oberdiek/hobsub-hyperref.sty
(/home/yigal/.texlive/2015/texmf-dist/tex/generic/oberdiek/hobsub-generic.sty))
 (/home/yigal/.texlive/2015/texmf-dist/tex/latex/oberdiek/auxhook.sty)
(/home/yigal/.texlive/2015/texmf-dist/tex/latex/hyperref/pd1enc.def)
(/home/yigal/.texlive/2015/texmf-dist/tex/latex/latexconfig/hyperref.cfg)
(/home/yigal/.texlive/2015/texmf-dist/tex/latex/url/url.sty))

Package hyperref Message: Driver (autodetected): hpdftex.

(/home/yigal/.texlive/2015/texmf-dist/tex/latex/hyperref/hpdftex.def
(/home/yigal/.texlive/2015/texmf-dist/tex/latex/oberdiek/rerunfilecheck.sty))
(/home/yigal/.texlive/2015/texmf-dist/tex/latex/tools/longtable.sty)
(/home/yigal/.texlive/2015/texmf-dist/tex/latex/booktabs/booktabs.sty)
(./Stroop Effect.aux)
(/home/yigal/.texlive/2015/texmf-dist/tex/context/base/supp-pdf.mkii
[Loading MPS to PDF converter (version 2006.09.02).]
) (/home/yigal/.texlive/2015/texmf-dist/tex/latex/oberdiek/epstopdf-base.sty
(/home/yigal/.texlive/2015/texmf-dist/tex/latex/oberdiek/grfext.sty)
(/home/yigal/.texlive/2015/texmf-dist/tex/latex/latexconfig/epstopdf-sys.cfg))
*geometry* driver: auto-detecting
*geometry* detected driver: pdftex

Package geometry Warning: The marginal notes overrun the paper.
     Add 3.73001pt and more to the right margin.

*geometry* verbose mode - [ preamble ] result:
* driver: pdftex
* paper: <default>
* layout: <same size as paper>
* layoutoffset:(h,v)=(0.0pt,0.0pt)
* modes: 
* h-part:(L,W,R)=(72.26999pt, 469.75502pt, 72.26999pt)
* v-part:(T,H,B)=(72.26999pt, 650.43001pt, 72.26999pt)
* \textbackslash{}paperwidth=614.295pt
* \textbackslash{}paperheight=794.96999pt
* \textbackslash{}textwidth=469.75502pt
* \textbackslash{}textheight=650.43001pt
* \textbackslash{}oddsidemargin=0.0pt
* \textbackslash{}evensidemargin=0.0pt
* \textbackslash{}topmargin=-37.0pt
* \textbackslash{}headheight=12.0pt
* \textbackslash{}headsep=25.0pt
* \textbackslash{}topskip=10.0pt
* \textbackslash{}footskip=30.0pt
* \textbackslash{}marginparwidth=65.0pt
* \textbackslash{}marginparsep=11.0pt
* \textbackslash{}columnsep=10.0pt
* \textbackslash{}skip\textbackslash{}footins=9.0pt plus 4.0pt minus 2.0pt
* \textbackslash{}hoffset=0.0pt
* \textbackslash{}voffset=0.0pt
* \textbackslash{}mag=1000
* \textbackslash{}@twocolumnfalse
* \textbackslash{}@twosidefalse
* \textbackslash{}@mparswitchfalse
* \textbackslash{}@reversemarginfalse
* (1in=72.27pt=25.4mm, 1cm=28.453pt)

(/home/yigal/.texlive/2015/texmf-dist/tex/latex/ucs/ucsencs.def)
(/home/yigal/.texlive/2015/texmf-dist/tex/latex/hyperref/nameref.sty
(/home/yigal/.texlive/2015/texmf-dist/tex/generic/oberdiek/gettitlestring.sty))
(./Stroop Effect.out) (./Stroop Effect.out)
(/home/yigal/.texlive/2015/texmf-dist/tex/latex/amsfonts/umsa.fd)
(/home/yigal/.texlive/2015/texmf-dist/tex/latex/amsfonts/umsb.fd)
(/home/yigal/.texlive/2015/texmf-dist/tex/latex/ucs/data/uni-32.def) [1\{/home/y
igal/.texlive/2015/texmf-var/fonts/map/pdftex/updmap/pdftex.map\}] [2] [3]
<Stroop Effect\_files/Stroop Effect\_9\_1.png, id=62, 571.13374pt x 499.8675pt>
<use Stroop Effect\_files/Stroop Effect\_9\_1.png>
Underfull \textbackslash{}hbox (badness 10000) in paragraph at lines 442--443

[4 <./Stroop Effect\_files/Stroop Effect\_9\_1.png>]
Underfull \textbackslash{}hbox (badness 10000) in paragraph at lines 468--471
[]\textbackslash{}OT1/cmr/m/n/10 https://docs.google.com/document/d/1bqyi1Fm5truesLhmbAq16Zl-A
jj9bnNIU[]68P60nDQg/pub \#

LaTeX Font Warning: Font shape `OMS/cmtt/m/n' undefined
(Font)              using `OMS/cmsy/m/n' instead
(Font)              for symbol `textbackslash' on input line 488.

[5] [6] [7] [8] [9] [10] [11] (./Stroop Effect.bbl) [12] (./Stroop Effect.aux)

LaTeX Font Warning: Some font shapes were not available, defaults substituted.

 )
(see the transcript file for additional information)</home/yigal/.texlive/2015/
texmf-dist/fonts/type1/public/amsfonts/cm/cmbx10.pfb></home/yigal/.texlive/2015
/texmf-dist/fonts/type1/public/amsfonts/cm/cmbx12.pfb></home/yigal/.texlive/201
5/texmf-dist/fonts/type1/public/amsfonts/cm/cmitt10.pfb></home/yigal/.texlive/2
015/texmf-dist/fonts/type1/public/amsfonts/cm/cmmi10.pfb></home/yigal/.texlive/
2015/texmf-dist/fonts/type1/public/amsfonts/cm/cmmi7.pfb></home/yigal/.texlive/
2015/texmf-dist/fonts/type1/public/amsfonts/cm/cmr10.pfb></home/yigal/.texlive/
2015/texmf-dist/fonts/type1/public/amsfonts/cm/cmr12.pfb></home/yigal/.texlive/
2015/texmf-dist/fonts/type1/public/amsfonts/cm/cmr17.pfb></home/yigal/.texlive/
2015/texmf-dist/fonts/type1/public/amsfonts/cm/cmr7.pfb></home/yigal/.texlive/2
015/texmf-dist/fonts/type1/public/amsfonts/cm/cmsy10.pfb></home/yigal/.texlive/
2015/texmf-dist/fonts/type1/public/amsfonts/cm/cmti10.pfb></home/yigal/.texlive
/2015/texmf-dist/fonts/type1/public/amsfonts/cm/cmtt10.pfb>
Output written on "Stroop Effect.pdf" (12 pages, 184279 bytes).
Transcript written on "Stroop Effect.log".
    \end{Verbatim}

    \begin{Verbatim}[commandchars=\\\{\}]
/home/yigal/.local/lib/python3.4/site-packages/IPython/nbconvert.py:13: ShimWarning: The `IPython.nbconvert` package has been deprecated. You should import from ipython\_nbconvert instead.
  "You should import from ipython\_nbconvert instead.", ShimWarning)
[NbConvertApp] Converting notebook Stroop Effect.ipynb to latex
[NbConvertApp] Support files will be in Stroop Effect\_files/
[NbConvertApp] Making directory Stroop Effect\_files
[NbConvertApp] Writing 48472 bytes to Stroop Effect.tex
    \end{Verbatim}

    \begin{Verbatim}[commandchars=\\\{\}]
{\color{incolor}In [{\color{incolor} }]:} \PY{o}{\PYZpc{}}\PY{k}{ls}
\end{Verbatim}

    \begin{Verbatim}[commandchars=\\\{\}]
{\color{incolor}In [{\color{incolor} }]:} \PY{c}{\PYZsh{}from notebook.nbextensions import install\PYZus{}nbextension}
        \PY{c}{\PYZsh{}install\PYZus{}nbextension(\PYZsq{}https://goo.gl/5TK96v\PYZsq{}, user=True, destination=\PYZdq{}vim\PYZus{}binding.js\PYZdq{})}
        \PY{c}{\PYZsh{} Or if you prefre a full URL}
        \PY{c}{\PYZsh{}install\PYZus{}nbextension(\PYZsq{}https://rawgithub.com/lambdalisue/jupyter\PYZhy{}vim\PYZhy{}binding/master/nbextensions/vim\PYZus{}binding.js\PYZsq{}, user=True)}
        \PY{c}{\PYZsh{}Jupyter.utils.load\PYZus{}extensions(\PYZsq{}vim\PYZus{}binding\PYZsq{})}
\end{Verbatim}

    \begin{Verbatim}[commandchars=\\\{\}]
{\color{incolor}In [{\color{incolor} }]:} \PY{o}{\PYZpc{}\PYZpc{}}\PY{k}{javascript}
        require([\PYZsq{}base/js/utils\PYZsq{}],
        function(utils) \PYZob{}
           utils.load\PYZus{}extensions(\PYZsq{}calico\PYZhy{}spell\PYZhy{}check\PYZsq{}, \PYZsq{}calico\PYZhy{}document\PYZhy{}tools\PYZsq{}, \PYZsq{}calico\PYZhy{}cell\PYZhy{}tools\PYZsq{});
        \PYZcb{});
\end{Verbatim}

    \begin{Verbatim}[commandchars=\\\{\}]
{\color{incolor}In [{\color{incolor} }]:} 
\end{Verbatim}


    % Add a bibliography block to the postdoc
    
    
\bibliographystyle{unsrt}
\bibliography{udacity}

    
    \end{document}
